\documentclass[11pt,a4paper,roman]{moderncv}
  \moderncvstyle{banking}
  \moderncvcolor{green}
  \nopagenumbers{}
  \usepackage[scale=0.9]{geometry}
  \usepackage{color}
  \newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
    {\bfseries #5}
  \end{tabular}\\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
    {\itshape #2}
  \end{tabular}
  \ifx&#7&
  \else{
    \begin{minipage}{\maincolumnwidth}
      \footnotesize #7
    \end{minipage}}\fi
  \par\addvspace{#1}
  }
  \newcommand*{\customcvproject}[4][.25em]{
  \begin{tabular}{@{}l} 
    {\small\bfseries #2} 
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
    {\footnotesize\itshape #3}
  \end{tabular}
  \ifx&#4&
  \else{\
    \begin{minipage}{\maincolumnwidth}%
      \footnotesize #4
    \end{minipage}}\fi
  \par\addvspace{#1}
  }
  \setlength{\tabcolsep}{12pt}
  
  \name{Alex}{Taylor}
  \address{12345 Folks Avenue, V7B 7X7, Vancouver, BC, Canada         }
  \begin{document}
  \makecvtitle
  \vspace*{-23mm}
  
  \begin{center}
  \begin{tabular}{ c c c }\faLanguage\enspace English, Spanish& \faEnvelopeO\enspace alex.taylor@email.com& \faMobile\enspace +1 (604) 123-4567 \\
  \end{tabular}
  \end{center}
  
  \section{ABOUT}
  Enthusiastic and innovative software engineer with a passion for developing user-centric applications and a knack for problem-solving. Seeking challenging opportunities to apply my skills in a dynamic team environment. 
  \section{SKILLS}
\textbf{Programming:} Python, Java, JavaScript, React, Node.js\\
\textbf{Data:} SQL, NoSQL, Firebase, Pandas, Numpy\\
\textbf{Miscellaneous:} Git, Docker, Kubernetes, Agile, Scrum
\section{EDUCATION}
\customcventry{2019 - 2023}{B.Sc. in Software Engineering}{University of British Columbia}{}{}{Focused on web and mobile applications development; expected graduation in May 2023.}
\section{WORK EXPERIENCE}
\customcventry{2022 - Present}{Software Developer Intern}{Innovate Tech}{Vancouver, BC}{}{{
      \begin{itemize}
        \item Developed and optimized web applications, improving user experience and performance.
\item Collaborated with cross-functional teams to define, design, and ship new features.
\item Assisted in the integration of back-end services with JavaScript-based front ends
      \end{itemize}
    }}
\customcventry{2021 - 2022}{Junior Web Developer}{Creative Solutions}{Vancouver, BC}{}{{
      \begin{itemize}
        \item Contributed to several high-profile client projects, focusing on frontend technologies.
\item Implemented responsive web design principles to ensure websites render well across multiple devices.
\item Participated in code reviews and collaborated with senior developers to enhance code quality.
\item 
      \end{itemize}
    }}
\section{PROJECTS}
\customcvproject{E-Commerce Website}{}{{
      \begin{itemize}
        \item Developed a full-stack e-commerce website using React and Node.js.
\item Implemented features like product listing, a shopping cart, and secure checkout.
      \end{itemize}
    }}
\customcvproject{Mobile Fitness App}{}{{
      \begin{itemize}
        \item Created a fitness tracking app with personalized workout and diet plans.
\item Utilized Firebase for user authentication and data storage.
      \end{itemize}
    }}

  \end{document}
  