\documentclass[11pt,a4paper,roman]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{green}
\nopagenumbers{}
\usepackage[scale=0.9]{geometry}
\usepackage{color}
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular}\\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&
  \else{
    \begin{minipage}{\maincolumnwidth}
      \footnotesize #7
    \end{minipage}}\fi
  \par\addvspace{#1}
}
\newcommand*{\customcvproject}[4][.25em]{
  \begin{tabular}{@{}l} 
    {\small\bfseries #2} 
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
     {\footnotesize\itshape #3}
  \end{tabular}
  \ifx&#4&
  \else{\
    \begin{minipage}{\maincolumnwidth}%
      \footnotesize #4
    \end{minipage}}\fi
  \par\addvspace{#1}
}
\setlength{\tabcolsep}{12pt}
%%%%%

\name{Alex}{Taylor}
\address{1234 Folks Avenue, Vancouver, BC, V7B 7X7, Canada}
\begin{document}
\makecvtitle
\vspace*{-23mm}
\begin{center}
\begin{tabular}{ c c c }
\faLanguage\enspace English, Spanish & \faEnvelopeO\enspace alex.taylor@email.com & \faMobile\enspace +1 (604) 123-4567 \\
\end{tabular}
\end{center}

\section{ABOUT}
Enthusiastic and innovative software engineer with a passion for developing user-centric applications and a knack for problem-solving. Seeking challenging opportunities to apply my skills in a dynamic team environment.

\section{SKILLS}
\textbf{Programming:} Python, Java, JavaScript, React, Node.js\\
\textbf{Data:} SQL, NoSQL, Firebase, Pandas, Numpy\\
\textbf{Miscellaneous:} Git, Docker, Kubernetes, Agile, Scrum

\section{EDUCATION}
\customcventry{2019 - 2023}{B.Sc. in Software Engineering}{University of British Columbia}{Vancouver, BC}{}{Focused on web and mobile application development; expected graduation in May 2023.}

\section{WORK EXPERIENCE}
\customcventry{2022 - Present}{Software Developer Intern}{Innovate Tech}{Vancouver, BC}{}{
    \begin{itemize}
        \item Developed and optimized web applications, improving user experience and performance.
        \item Collaborated with cross-functional teams to define, design, and ship new features.
        \item Assisted in the integration of back-end services with JavaScript-based front ends.
    \end{itemize}
}
\customcventry{2021 - 2022}{Junior Web Developer}{Creative Solutions}{Vancouver, BC}{}{
    \begin{itemize}
        \item Contributed to several high-profile client projects, focusing on frontend technologies.
        \item Implemented responsive web design principles to ensure websites render well across multiple devices.
        \item Participated in code reviews and collaborated with senior developers to enhance code quality.
    \end{itemize}
}

\section{PROJECTS}
\customcvproject{E-Commerce Website}{2021}{}{
    \begin{itemize}
        \item Developed a full-stack e-commerce website using React and Node.js.
        \item Implemented features like product listing, a shopping cart, and secure checkout.
    \end{itemize}
}
\customcvproject{Mobile Fitness App}{2022}{}{
    \begin{itemize}
        \item Created a fitness tracking app with personalized workout and diet plans.
        \item Utilized Firebase for user authentication and data storage.
    \end{itemize}
}

\end{document}

\documentclass[11pt,a4paper,roman]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{green}
\nopagenumbers{}
\usepackage[scale=0.9]{geometry}
\usepackage{color}
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular}\\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&
  \else{
    \begin{minipage}{\maincolumnwidth}
      \footnotesize #7
    \end{minipage}}\fi
  \par\addvspace{#1}
}
\newcommand*{\customcvproject}[4][.25em]{
  \begin{tabular}{@{}l} 
    {\small\bfseries #2} 
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
     {\footnotesize\itshape #3}
  \end{tabular}
  \ifx&#4&
  \else{\
    \begin{minipage}{\maincolumnwidth}%
      \footnotesize #4
    \end{minipage}}\fi
  \par\addvspace{#1}
}
\setlength{\tabcolsep}{12pt}


\name{Sarah}{Johnson}
\address{5678 Maple Road, Toronto, ON, M4B 1P3, Canada}

\begin{document}
\makecvtitle
\vspace*{-23mm}

\begin{center}
\begin{tabular}{ c c c }
\faLanguage\enspace English, French & \faEnvelopeO\enspace sarah.johnson@email.com & \faMobile\enspace +1 (555) 123-4567 \\
\end{tabular}
\end{center}

\section{ABOUT}
Dynamic and results-oriented project manager with extensive experience in managing large-scale projects in the IT sector. Adept at team leadership, problem-solving, and ensuring projects are delivered on time and within budget.

\section{SKILLS}
\textbf{Project Management:} Agile, Scrum, Waterfall, Kanban\\
\textbf{Tools:} JIRA, Asana, MS Project, Trello\\
\textbf{Collaboration:} Slack, Microsoft Teams, Zoom\\
\textbf{Miscellaneous:} MS Office, Risk Management, Budgeting

\section{EDUCATION}
\customcventry{2015 - 2019}{Bachelor of Business Administration}{University of Toronto}{Toronto, ON}{}{Specialization in Project Management and Operations.}

\section{WORK EXPERIENCE}
\customcventry{2021 - Present}{Senior Project Manager}{Tech Innovators}{Toronto, ON}{}{
    \begin{itemize}
        \item Lead project teams to deliver technology solutions that meet client needs and company objectives.
        \item Developed project plans, schedules, and work breakdown structures.
        \item Managed budgets up to $2M, ensuring projects are delivered within cost constraints.
    \end{itemize}
}
\customcventry{2019 - 2021}{Project Coordinator}{Digital Solutions Inc.}{Toronto, ON}{}{
    \begin{itemize}
        \item Assisted in the management of multiple IT projects, coordinating between cross-functional teams.
        \item Played a key role in project planning, execution, monitoring, and closure.
        \item Prepared regular project status reports and presentations for stakeholders.
    \end{itemize}
}

\section{PROJECTS}
\customcvproject{Enterprise Resource Planning (ERP) System Implementation}{2020}{}{
    \begin{itemize}
        \item Managed the successful implementation of an ERP system for a mid-size manufacturing company.
        \item Coordinated with software vendors, IT staff, and end-users for smooth system integration.
    \end{itemize}
}
\customcvproject{Website Redesign Project}{2021}{}{
    \begin{itemize}
        \item Oversaw the redesign of a corporate website, enhancing functionality and user experience.
        \item Worked closely with designers, developers, and marketing teams to align the website with company branding.
    \end{itemize}
}

\end{document}
