\documentclass[11pt,a4paper,roman]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}
\nopagenumbers{}
\usepackage[scale=0.9]{geometry}
\usepackage{color}
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
     {\bfseries #5}
  \end{tabular}\\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
     {\itshape #2}
  \end{tabular}
  \ifx&#7&
  \else{
    \begin{minipage}{\maincolumnwidth}
      \footnotesize #7
    \end{minipage}}\fi
  \par\addvspace{#1}
}
\newcommand*{\customcvproject}[4][.25em]{
  \begin{tabular}{@{}l} 
    {\small\bfseries #2} 
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
     {\footnotesize\itshape #3}
  \end{tabular}
  \ifx&#4&
  \else{\
    \begin{minipage}{\maincolumnwidth}%
      \footnotesize #4
    \end{minipage}}\fi
  \par\addvspace{#1}
}
\setlength{\tabcolsep}{12pt}
%%%%%

\name{Michael}{Lee}
\address{1987 Fellas Road, Ottawa, ON, K1R 1R1, Canada}
\begin{document}
\makecvtitle
\vspace*{-23mm}
\begin{center}
\begin{tabular}{ c c c c }
\faLanguage\enspace English, French & \faEnvelopeO\enspace michael.lee@email.com & \href{https://github.com/michaellee}{\faGithub} & \faMobile\enspace +1 (555) 123-4567 \\
\end{tabular}
\end{center}

\section{ABOUT}
Experienced software developer with a strong background in full-stack development, especially in web technologies. Eager to apply my expertise in a challenging and innovative environment.

\section{SKILLS}
\textbf{Programming:} JavaScript, Python, Java, C\#\\
\textbf{Web Development:} React, Angular, Node.js, Django\\
\textbf{Databases:} MySQL, MongoDB, PostgreSQL\\
\textbf{Tools:} Git, Docker, Jenkins, AWS

\section{EDUCATION}
\customcventry{2016 - 2020}{B.Sc. in Computer Science}{University of British Columbia}{Vancouver, BC}{}{Specialized in software development and web technologies.}
\customcventry{2019 - 2020}{Diploma in Full-Stack Web Development}{BCIT}{Vancouver, BC}{}{Focused on modern web development frameworks and best practices.}

\section{WORK EXPERIENCE}
\customcventry{2020 - Present}{Software Developer}{InnovateX}{Vancouver, BC}{}{
    \begin{itemize}
        \item Developed and maintained scalable web applications for various clients.
        \item Led a team in creating a highly successful e-commerce platform.
        \item Collaborated closely with UX/UI designers to implement user-friendly interfaces.
    \end{itemize}
}
\customcventry{2019 - 2020}{Intern Developer}{WebTech Solutions}{Vancouver, BC}{}{
    \begin{itemize}
        \item Assisted in the development of several web applications using React and Node.js.
        \item Participated in agile development cycles and code reviews.
        \item Implemented RESTful APIs and integrated third-party services.
    \end{itemize}
}

\section{PROJECTS}
\customcvproject{Social Media Analytics Tool}{2019}{}{
    \begin{itemize}
        \item Developed a tool for analyzing social media trends and user engagement.
        \item Utilized machine learning algorithms for sentiment analysis and data visualization.
    \end{itemize}
}
\customcvproject{Online Learning Platform}{2020}{}{
    \begin{itemize}
        \item Created an online learning platform with features for course management and student interaction.
        \item Implemented adaptive learning algorithms to personalize content for users.
    \end{itemize}
}

\end{document}