
  \documentclass[letterpaper,11pt]{article}
  \usepackage[empty]{fullpage}
  \usepackage{titlesec}
  \usepackage[usenames,dvipsnames]{color}
  \usepackage{enumitem}
  \usepackage[hidelinks]{hyperref}
  \usepackage[english]{babel}
  \usepackage{tabularx}
  \addtolength{\oddsidemargin}{-0.5in}
  \addtolength{\evensidemargin}{-0.5in}
  \addtolength{\textwidth}{1in}
  \addtolength{\topmargin}{-.5in}
  \addtolength{\textheight}{1.0in}
  \urlstyle{same}
  \raggedbottom
  \raggedright
  \setlength{\tabcolsep}{0in}
  \titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
  }{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]
  \newcommand{\resumeItem}[1]{
    \item\small{
      {#1 \vspace{-2pt}}
    }
  }
  \newcommand{\resumeSubheading}[5]{
    \vspace{-2pt}\item
      \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
      \end{tabular*}
      {#5}\\}
  \newcommand{\resumeSubheadingBis}[4]{
    \vspace{-2pt}\item
      \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
      \end{tabular*}\vspace{-7pt}}
  \newcommand{\resumeSubSubheading}[2]{
      \item
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \
      \end{tabular*}\vspace{-7pt}}
  \newcommand{\resumeProjectHeading}[2]{
      \item
      \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & #2 \
      \end{tabular*}\vspace{-7pt}}
  \newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}
  \renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
  \newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
  \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
  \newcommand{\resumeSkillsListStart}{\begin{itemize}[leftmargin=0.15in, label={}, noitemsep, topsep=0pt, partopsep=0pt]}
  \newcommand{\resumeSkillsListEnd}{\end{itemize}}  
  \newcommand{\resumeItemListStart}{\begin{itemize}}
  \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
  \begin{document}
  
  \begin{center}
  \textbf{\Huge \scshape Alex Taylor} \\ \vspace{1pt}\small +1 (604) 123-4567 $|$ \href{mailto:alex.taylor@email.com}{{alex.taylor@email.com}}\end{center}
    \section{About}
    Enthusiastic and innovative software engineer with a passion for developing user-centric applications and a knack for problem-solving. Seeking challenging opportunities to apply my skills in a dynamic team environment. 
    \section{Skills}
    \resumeSkillsListStart
        \item\textbf{Programming:} Python, Java, JavaScript, React, Node.js\\
\item\textbf{Data:} SQL, NoSQL, Firebase, Pandas, Numpy\\
\item\textbf{Miscellaneous:} Git, Docker, Kubernetes, Agile, Scrum
    \resumeSubHeadingListEnd
    \section{Education}
    \resumeSubHeadingListStart
          \resumeSubheading
            {University of British Columbia}{}
            {B.Sc. in Software Engineering}{2019 - 2023}{Focused on web and mobile applications development; expected graduation in May 2023.}
    \resumeSubHeadingListEnd
      \section{Experience}
      \resumeSubHeadingListStart
          \resumeSubheadingBis
            {Software Developer Intern}{2022 - Present}
            {Innovate Tech}{Vancouver, BC}{
            \resumeItemListStart\resumeItem{Developed and optimized web applications, improving user experience and performance.}
\resumeItem{Collaborated with cross-functional teams to define, design, and ship new features.}
\resumeItem{Assisted in the integration of back-end services with JavaScript-based front ends}

            \resumeItemListEnd}
          \resumeSubheadingBis
            {Junior Web Developer}{2021 - 2022}
            {Creative Solutions}{Vancouver, BC}{
            \resumeItemListStart\resumeItem{Contributed to several high-profile client projects, focusing on frontend technologies.}
\resumeItem{Implemented responsive web design principles to ensure websites render well across multiple devices.}
\resumeItem{Participated in code reviews and collaborated with senior developers to enhance code quality.}

            \resumeItemListEnd}
      \resumeSubHeadingListEnd
      \section{Projects}
      \resumeSubHeadingListStart
          \resumeProjectHeading
            {\textbf{E-Commerce Website}}{}\resumeItemListStart\resumeItem{Developed a full-stack e-commerce website using React and Node.js.}
\resumeItem{Implemented features like product listing, a shopping cart, and secure checkout.}
\resumeItemListEnd
          \resumeProjectHeading
            {\textbf{Mobile Fitness App}}{}\resumeItemListStart\resumeItem{Created a fitness tracking app with personalized workout and diet plans.}
\resumeItem{Utilized Firebase for user authentication and data storage.}
\resumeItemListEnd
      \resumeSubHeadingListEnd
    \end{document}