\documentclass[a4paper,8pt]{article}
  \usepackage{parskip}
  \usepackage{hologo}
  \usepackage{fontspec}
  \RequirePackage{color}
  \RequirePackage{graphicx}
  \usepackage[usenames,dvipsnames]{xcolor}
  \usepackage[scale=0.9, top=.4in, bottom=.4in]{geometry}
  \usepackage{tabularx}
  \usepackage{enumitem}
  \newcolumntype{C}{>{\centering\arraybackslash}X}
  \usepackage{supertabular}
  \usepackage{tabularx}
  \newlength{\fullcollw}
  \setlength{\fullcollw}{0.42\textwidth}
  \usepackage{titlesec}
  \usepackage{multicol}
  \usepackage{multirow}
  \titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
  \titlespacing{\section}{1pt}{2pt}{2pt}
  \usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
  \usepackage[unicode, draft=false]{hyperref}
  \usepackage{fontawesome5}
  \usepackage[normalem]{ulem}
  \setmainfont{TeX Gyre Heros}
  \setlist[itemize]{label={-}, itemsep=0pt, parsep=0pt, topsep=0pt, partopsep=0pt, leftmargin=1em}

  
  % Define colors based on input
  \definecolor{headerColor}{HTML}{324E2E}
  \definecolor{subHeaderColor}{HTML}{4A7344}
  
  % commands for entries
  \newcommand{\entryItems}[4]{
    \noindent\textbf{\color{headerColor}#1}\hfill\textbf{\color{subHeaderColor}#2}
    \ifx&#3&\else\\\noindent\textit{\color{subHeaderColor}#3}\fi
      #4
    \vspace{5pt} % Adjust vertical space after each entry
  }
  \newcommand{\entry}[4]{
    \noindent\textbf{\color{headerColor}#1}\hfill\textbf{\color{subHeaderColor}#2}
    \ifx&#3&\else\\\noindent\textit{\color{subHeaderColor}#3}\fi
      \\#4
    \vspace{5pt} % Adjust vertical space after each entry
  }
  \begin{document}
  \pagestyle{empty}
  
  \begin{tabularx}{\linewidth}{@{} C @{}}
  
  \color{headerColor} \Huge{Alex Taylor} \\[6pt]\\
  \textcolor{subHeaderColor}{\raisebox{-0.05\height}{\faLanguage} English, Spanish }
\textcolor{subHeaderColor}{\raisebox{-0.05\height}{\faMobile} +1 (604) 123-4567 }
\\\textcolor{subHeaderColor}{\raisebox{-0.05\height}{\faMapMarker} 12345 Folks Avenue, V7B 7X7, Vancouver, BC, Canada          }
\textcolor{subHeaderColor}{{\href{mailto:alex.taylor@email.com}{\raisebox{-0.05\height}{\faEnvelope} alex.taylor@email.com}} }
\end{tabularx}
\color{headerColor}\section{About}\vspace{1ex}\color{black}{Enthusiastic and innovative software engineer with a passion for developing user-centric applications and a knack for problem-solving. Seeking challenging opportunities to apply my skills in a dynamic team environment. }\color{headerColor}\section{Skills}
\vspace{1ex}
  \color{headerColor}\textbf{Programming:} \color{black} Python, Java, JavaScript, React, Node.js
\\
  \color{headerColor}\textbf{Data:} \color{black} SQL, NoSQL, Firebase, Pandas, Numpy
\\
  \color{headerColor}\textbf{Miscellaneous:} \color{black} Git, Docker, Kubernetes, Agile, Scrum

  \color{headerColor}\section{Education}
\vspace{1ex}
  \entry{University of British Columbia}
      {2019 - 2023}
      {B.Sc. in Software Engineering}
      {\textcolor{black}{Focused on web and mobile applications development; expected graduation in May 2023.}}

  \color{headerColor}\section{Work Experience}
\vspace{1ex}\entryItems{Innovate Tech}{2022 - Present}{Software Developer Intern}{\textcolor{black}{{
      \begin{itemize}
        \item Developed and optimized web applications, improving user experience and performance.
\item Collaborated with cross-functional teams to define, design, and ship new features.
\item Assisted in the integration of back-end services with JavaScript-based front ends
      \end{itemize}
    }}}
\entryItems{Creative Solutions}{2021 - 2022}{Junior Web Developer}{\textcolor{black}{{
      \begin{itemize}
        \item Contributed to several high-profile client projects, focusing on frontend technologies.
\item Implemented responsive web design principles to ensure websites render well across multiple devices.
\item Participated in code reviews and collaborated with senior developers to enhance code quality.
\item 
      \end{itemize}
    }}}
\color{headerColor}\section{Projects}
\vspace{1ex}\entryItems{E-Commerce Website}{}{}{\textcolor{black}{{
      \begin{itemize}
        \item Developed a full-stack e-commerce website using React and Node.js.
\item Implemented features like product listing, a shopping cart, and secure checkout.
      \end{itemize}
    }}}
\entryItems{Mobile Fitness App}{}{}{\textcolor{black}{{
      \begin{itemize}
        \item Created a fitness tracking app with personalized workout and diet plans.
\item Utilized Firebase for user authentication and data storage.
      \end{itemize}
    }}}

  \end{document}