\documentclass[a4paper,8pt]{article}
  \usepackage{parskip}
  \usepackage{hologo}
  \usepackage{fontspec}
  \RequirePackage{color}
  \RequirePackage{graphicx}
  \usepackage[usenames,dvipsnames]{xcolor}
  \usepackage[scale=0.9, top=.4in, bottom=.4in]{geometry}
  \usepackage{tabularx}
  \usepackage{enumitem}
  \newcolumntype{C}{>{\centering\arraybackslash}X}
  \usepackage{supertabular}
  \usepackage{tabularx}
  \newlength{\fullcollw}
  \setlength{\fullcollw}{0.42\textwidth}
  \usepackage{titlesec}
  \usepackage{multicol}
  \usepackage{multirow}
  \titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
  \titlespacing{\section}{1pt}{2pt}{2pt}
  \usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
  \usepackage[unicode, draft=false]{hyperref}
  \usepackage{fontawesome5}
  \usepackage[normalem]{ulem}
  \setmainfont{TeX Gyre Heros}
  \setlist[itemize]{label={-}, itemsep=0pt, parsep=0pt, topsep=0pt, partopsep=0pt, leftmargin=1em}

  
  % Define colors based on input
  \definecolor{headerColor}{HTML}{400305}
  \definecolor{subHeaderColor}{HTML}{831014}
  
  % commands for entries
  \newcommand{\entryItems}[4]{
    \noindent\textbf{\color{headerColor}#1}\hfill\textbf{\color{subHeaderColor}#2}
    \ifx&#3&\else\\\noindent\textit{\color{subHeaderColor}#3}\fi
      #4
    \vspace{5pt} % Adjust vertical space after each entry
  }
  \newcommand{\entry}[4]{
    \noindent\textbf{\color{headerColor}#1}\hfill\textbf{\color{subHeaderColor}#2}
    \ifx&#3&\else\\\noindent\textit{\color{subHeaderColor}#3}\fi
      \\#4
    \vspace{5pt} % Adjust vertical space after each entry
  }
  \begin{document}
  \pagestyle{empty}
  
  \begin{tabularx}{\linewidth}{@{} C @{}}
  
  \color{headerColor} \Huge{Emily Chen} \\[6pt]\\
  \textcolor{subHeaderColor}{\raisebox{-0.05\height}{\faLanguage} English, Mandarin }
\textcolor{subHeaderColor}{\raisebox{-0.05\height}{\faMobile} +1 (555) 123-4567 }
\textcolor{subHeaderColor}{{\href{https://github.com/emilychen}{\raisebox{-0.05\height}{\faGithub}}} }
\\\textcolor{subHeaderColor}{\raisebox{-0.05\height}{\faMapMarker} 2564 Brothers Avenue, M5O 5K5, Toronto, ON, Canada          }
\textcolor{subHeaderColor}{{\href{mailto:emily.chen@email.com}{\raisebox{-0.05\height}{\faEnvelope} emily.chen@email.com}} }
\end{tabularx}
\color{headerColor}\section{About}\vspace{1ex}\color{black}{As a data analyst with a strong background in statistical modeling and data visualization, I am seeking opportunities to leverage my skills in data-driven decision making and insights generation.}\color{headerColor}\section{Skills}
\vspace{1ex}
  \color{headerColor}\textbf{Programming:} \color{black} Python, R, SQL, Julia
\\
  \color{headerColor}\textbf{Data:} \color{black} Machine Learning, Data Visualization, Big Data
\\
  \color{headerColor}\textbf{Tools:} \color{black} Tableau, Power BI, Excel, Jupyter
\\
  \color{headerColor}\textbf{Miscellaneous:} \color{black} Git, Data Mining, Predictive Modeling, Agile

  \color{headerColor}\section{Education}
\vspace{1ex}
  \entry{University of Toronto}
      {2018 - 2022}
      {B.Sc. in Data Science}
      {\textcolor{black}{Graduated with honors, focusing on statistical methods and data analysis.}}

  \entry{Humber College}
      {2020-2021}
      {Diploma in Big Data Analytics}
      {\textcolor{black}{Concentrated on big data technologies and applications.}}

  \color{headerColor}\section{Work Experience}
\vspace{1ex}\entryItems{Insight Data Corp}{2022 - Present}{Data Analyst}{\textcolor{black}{{
      \begin{itemize}
        \item Analyzed large datasets to identify trends and insights that informed business decisions.
\item Developed and automated reporting processes using Python and SQL.
\item Collaborated with cross-functional teams to understand data needs and deliver comprehensive analyses.
      \end{itemize}
    }}}
\entryItems{Market Trends Inc}{2021 - 2022}{Junior Data Analyst}{\textcolor{black}{{
      \begin{itemize}
        \item Assisted in the development of data models and algorithms to predict market trends.
\item Utilized data visualization tools to present insights to stakeholders.
\item Contributed to the improvement of data collection and analysis processes.
\item 
      \end{itemize}
    }}}
\color{headerColor}\section{Projects}
\vspace{1ex}\entryItems{Sales Data Analysis}{}{}{\textcolor{black}{{
      \begin{itemize}
        \item Analyzed sales data to identify patterns and provide actionable insights for marketing strategy adjustments.
\item Employed statistical analysis techniques and machine learning models.
\item 
      \end{itemize}
    }}}
\entryItems{Customer Segmentation Study }{}{}{\textcolor{black}{{
      \begin{itemize}
        \item Conducted a comprehensive customer segmentation analysis for a retail company.
\item Implemented clustering algorithms to categorize customer groups based on purchasing behavior.
      \end{itemize}
    }}}

  \end{document}