\documentclass[a4paper,8pt]{article}
  \usepackage{parskip}
  \usepackage{hologo}
  \usepackage{fontspec}
  \RequirePackage{color}
  \RequirePackage{graphicx}
  \usepackage[usenames,dvipsnames]{xcolor}
  \usepackage[scale=0.9, top=.4in, bottom=.4in]{geometry}
  \usepackage{tabularx}
  \usepackage{enumitem}
  \newcolumntype{C}{>{\centering\arraybackslash}X}
  \usepackage{supertabular}
  \usepackage{tabularx}
  \newlength{\fullcollw}
  \setlength{\fullcollw}{0.42\textwidth}
  \usepackage{titlesec}
  \usepackage{multicol}
  \usepackage{multirow}
  \titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
  \titlespacing{\section}{1pt}{2pt}{2pt}
  \usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}
  \usepackage[unicode, draft=false]{hyperref}
  \usepackage{fontawesome5}
  \usepackage[normalem]{ulem}
  \setmainfont{TeX Gyre Heros}
  \setlist[itemize]{label={-}, itemsep=0pt, parsep=0pt, topsep=0pt, partopsep=0pt, leftmargin=1em}

  
  % Define colors based on input
  \definecolor{headerColor}{HTML}{19426e}
  \definecolor{subHeaderColor}{HTML}{00008b}
  
  % commands for entries
  \newcommand{\entryItems}[4]{
    \noindent\textbf{\color{headerColor}#1}\hfill\textbf{\color{subHeaderColor}#2}
    \ifx&#3&\else\\\noindent\textit{\color{subHeaderColor}#3}\fi
      #4
    \vspace{5pt} % Adjust vertical space after each entry
  }
  \newcommand{\entry}[4]{
    \noindent\textbf{\color{headerColor}#1}\hfill\textbf{\color{subHeaderColor}#2}
    \ifx&#3&\else\\\noindent\textit{\color{subHeaderColor}#3}\fi
      \\#4
    \vspace{5pt} % Adjust vertical space after each entry
  }
  \begin{document}
  \pagestyle{empty}
  
  \begin{tabularx}{\linewidth}{@{} C @{}}
  
  \color{headerColor} \Huge{Michael Lee} \\[6pt]\\
  \textcolor{subHeaderColor}{\raisebox{-0.05\height}{\faLanguage} English, French }
\textcolor{subHeaderColor}{\raisebox{-0.05\height}{\faMobile} +1 (888) 123-4567 }
\textcolor{subHeaderColor}{{\href{https://linkedin.com/michaellee}{\raisebox{-0.05\height}{\faLinkedin}}} }
\\\textcolor{subHeaderColor}{\raisebox{-0.05\height}{\faMapMarker} 1987 Fellas Road, K1R 1R1, Ottawa, ON, Canada          }
\textcolor{subHeaderColor}{{\href{mailto:michael.lee@email.com}{\raisebox{-0.05\height}{\faEnvelope} michael.lee@email.com}} }
\end{tabularx}
\color{headerColor}\section{About}\vspace{1ex}\color{black}{Experienced software developer with a strong background in full-stack development, especially in web technologies.
Eager to apply my expertise in a challenging and innovative environment.}\color{headerColor}\section{Skills}
\vspace{1ex}
  \color{headerColor}\textbf{Programming:} \color{black} Python, JavaScript, Java, C\#
\\
  \color{headerColor}\textbf{Web Development:} \color{black} React, Angular, Node.js, Django
\\
  \color{headerColor}\textbf{Databases:} \color{black} MySQL, MongoDB, PostgreSQL
\\
  \color{headerColor}\textbf{Tools:} \color{black} Git, Docker, Jenkins, AWS

  \color{headerColor}\section{Education}
\vspace{1ex}
  \entry{University of Ottawa}
      {2016 - 2020}
      {B.Sc. in Computer Science}
      {\textcolor{black}{Specialized in software development and web technologies.}}

  \entry{Gatineau College}
      {2019-2020}
      {Diploma in Full-Stack Web Development}
      {\textcolor{black}{Focused on modern web development frameworks and best practices.}}

  \color{headerColor}\section{Work Experience}
\vspace{1ex}\entryItems{InnovateX}{2020 - Present}{Data Analyst}{\textcolor{black}{{
      \begin{itemize}
        \item Developed and maintained scalable web applications for various clients.
\item Led a team in creating a highly successful e-commerce platform.
\item Collaborated closely with UX/UI designers to implement user-friendly interfaces.
      \end{itemize}
    }}}
\entryItems{WebTech Solutions}{2019 - 2020}{Junior Data Analyst}{\textcolor{black}{{
      \begin{itemize}
        \item Assisted in the development of several web applications using React and Node.js.
\item Participated in agile development cycles and code reviews.
\item Implemented RESTful APIs and integrated third-party services.
      \end{itemize}
    }}}
\color{headerColor}\section{Projects}
\vspace{1ex}\entryItems{Social Media Analytics Tool}{}{}{\textcolor{black}{{
      \begin{itemize}
        \item Developed a tool for analyzing social media trends and user engagement.
\item Utilized machine learning algorithms for sentiment analysis and data visualization.
      \end{itemize}
    }}}
\entryItems{Online Learning Platform}{}{}{\textcolor{black}{{
      \begin{itemize}
        \item Created an online learning platform with features for course management and student interaction.
\item Implemented adaptive learning algorithms to personalize content for users.
      \end{itemize}
    }}}

  \end{document}