\documentclass[11pt,a4paper,roman]{moderncv}
  \moderncvstyle{banking}
  \moderncvcolor{black}
  \nopagenumbers{}
  \usepackage[scale=0.9]{geometry}
  \usepackage{color}
  \newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
    {\bfseries #5}
  \end{tabular}\\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
    {\itshape #2}
  \end{tabular}
  \ifx&#7&
  \else{
    \begin{minipage}{\maincolumnwidth}
      \footnotesize #7
    \end{minipage}}\fi
  \par\addvspace{#1}
  }
  \newcommand*{\customcvproject}[4][.25em]{
  \begin{tabular}{@{}l} 
    {\small\bfseries #2} 
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
    {\footnotesize\itshape #3}
  \end{tabular}
  \ifx&#4&
  \else{\
    \begin{minipage}{\maincolumnwidth}%
      \footnotesize #4
    \end{minipage}}\fi
  \par\addvspace{#1}
  }
  \setlength{\tabcolsep}{12pt}
  
  \name{Emily}{Chen}
  \address{2564 Brothers Avenue, M5O 5K5, Toronto, ON, Canada         }
  \begin{document}
  \makecvtitle
  \vspace*{-23mm}
  
  \begin{center}
  \begin{tabular}{ c c c c }\faLanguage\enspace English, Mandarin& \faEnvelopeO\enspace emily.chen@email.com& \href{https://github.com/emilychen}{\faGithub} & \faMobile\enspace +1 (555) 123-4567 \\
  \end{tabular}
  \end{center}
  
  \section{ABOUT}
  As a data analyst with a strong background in statistical modeling and data visualization, I am seeking opportunities to leverage my skills in data-driven decision making and insights generation.
  \section{SKILLS}
\textbf{Programming:} Python, R, SQL, Julia\\
\textbf{Data:} Machine Learning, Data Visualization, Big Data\\
\textbf{Tools:} Tableau, Power BI, Excel, Jupyter\\
\textbf{Miscellaneous:} Git, Data Mining, Predictive Modeling, Agile
\section{EDUCATION}
\customcventry{2018 - 2022}{B.Sc. in Data Science}{University of Toronto}{}{}{Graduated with honors, focusing on statistical methods and data analysis.}
\customcventry{2020-2021}{Diploma in Big Data Analytics}{Humber College}{}{}{Concentrated on big data technologies and applications.}
\section{WORK EXPERIENCE}
\customcventry{2022 - Present}{Data Analyst}{Insight Data Corp}{Toronto, ON}{}{{
      \begin{itemize}
        \item Analyzed large datasets to identify trends and insights that informed business decisions.
\item Developed and automated reporting processes using Python and SQL.
\item Collaborated with cross-functional teams to understand data needs and deliver comprehensive analyses.
      \end{itemize}
    }}
\customcventry{2021 - 2022}{Junior Data Analyst}{Market Trends Inc}{Toronto, ON}{}{{
      \begin{itemize}
        \item Assisted in the development of data models and algorithms to predict market trends.
\item Utilized data visualization tools to present insights to stakeholders.
\item Contributed to the improvement of data collection and analysis processes.
\item 
      \end{itemize}
    }}
\section{PROJECTS}
\customcvproject{Sales Data Analysis}{}{{
      \begin{itemize}
        \item Analyzed sales data to identify patterns and provide actionable insights for marketing strategy adjustments.
\item Employed statistical analysis techniques and machine learning models.
\item 
      \end{itemize}
    }}
\customcvproject{Customer Segmentation Study }{}{{
      \begin{itemize}
        \item Conducted a comprehensive customer segmentation analysis for a retail company.
\item Implemented clustering algorithms to categorize customer groups based on purchasing behavior.
      \end{itemize}
    }}

  \end{document}
  