\documentclass[11pt,a4paper,roman]{moderncv}
  \moderncvstyle{banking}
  \moderncvcolor{blue}
  \nopagenumbers{}
  \usepackage[scale=0.9]{geometry}
  \usepackage{color}
  \newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4}
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
    {\bfseries #5}
  \end{tabular}\\
  \begin{tabular}{@{}l} 
    {\itshape #3}
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
    {\itshape #2}
  \end{tabular}
  \ifx&#7&
  \else{
    \begin{minipage}{\maincolumnwidth}
      \footnotesize #7
    \end{minipage}}\fi
  \par\addvspace{#1}
  }
  \newcommand*{\customcvproject}[4][.25em]{
  \begin{tabular}{@{}l} 
    {\small\bfseries #2} 
  \end{tabular}
  \hfill
  \begin{tabular}{l@{}}
    {\footnotesize\itshape #3}
  \end{tabular}
  \ifx&#4&
  \else{\
    \begin{minipage}{\maincolumnwidth}%
      \footnotesize #4
    \end{minipage}}\fi
  \par\addvspace{#1}
  }
  \setlength{\tabcolsep}{12pt}
  
  \name{Michael}{Lee}
  \address{1987 Fellas Road, K1R 1R1, Ottawa, ON, Canada         }
  \begin{document}
  \makecvtitle
  \vspace*{-23mm}
  
  \begin{center}
  \begin{tabular}{ c c c c }\faLanguage\enspace English, French& \faEnvelopeO\enspace michael.lee@email.com& \href{https://linkedin.com/michaellee}{\faLinkedinSquare} & \faMobile\enspace +1 (888) 123-4567 \\
  \end{tabular}
  \end{center}
  
  \section{ABOUT}
  Experienced software developer with a strong background in full-stack development, especially in web technologies.
Eager to apply my expertise in a challenging and innovative environment.
  \section{SKILLS}
\textbf{Programming:} Python, JavaScript, Java, C\#\\
\textbf{Web Development:} React, Angular, Node.js, Django\\
\textbf{Databases:} MySQL, MongoDB, PostgreSQL\\
\textbf{Tools:} Git, Docker, Jenkins, AWS
\section{EDUCATION}
\customcventry{2016 - 2020}{B.Sc. in Computer Science}{University of Ottawa}{}{}{Specialized in software development and web technologies.}
\customcventry{2019-2020}{Diploma in Full-Stack Web Development}{Gatineau College}{}{}{Focused on modern web development frameworks and best practices.}
\section{WORK EXPERIENCE}
\customcventry{2020 - Present}{Data Analyst}{InnovateX}{Ottawa, ON}{}{{
      \begin{itemize}
        \item Developed and maintained scalable web applications for various clients.
\item Led a team in creating a highly successful e-commerce platform.
\item Collaborated closely with UX/UI designers to implement user-friendly interfaces.
      \end{itemize}
    }}
\customcventry{2019 - 2020}{Junior Data Analyst}{WebTech Solutions}{Ottawa, ON}{}{{
      \begin{itemize}
        \item Assisted in the development of several web applications using React and Node.js.
\item Participated in agile development cycles and code reviews.
\item Implemented RESTful APIs and integrated third-party services.
      \end{itemize}
    }}
\section{PROJECTS}
\customcvproject{Social Media Analytics Tool}{}{{
      \begin{itemize}
        \item Developed a tool for analyzing social media trends and user engagement.
\item Utilized machine learning algorithms for sentiment analysis and data visualization.
      \end{itemize}
    }}
\customcvproject{Online Learning Platform}{}{{
      \begin{itemize}
        \item Created an online learning platform with features for course management and student interaction.
\item Implemented adaptive learning algorithms to personalize content for users.
      \end{itemize}
    }}

  \end{document}
  